Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-01-29 awipev-CO2.Rmd
minor language editing

## SNAPO-CO2
We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates.
Arbitrary, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1. In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1.
There are exceptions when it is difficult to decide which of the replicates need to be eliminated.

For TA, dupicates's flags that have been changed to 1 are:

@@

For CT, dupicates's flags that have been changed to 1 are:

@@

@@

###**TA analyser**
- **2019-01-26**: Philipp did the TA caibration: T0 with CRM 145.Beginning of a 3-months period. Flow filter was also lifted up and the saewater flow was rised up.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).

>>>>

## SNAPO-CO2
We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates. Arbitrarily, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1. In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1. There are exceptions when it is difficult to decide which of the replicates need to be eliminated.

For TA, dulpicates's flags that have been changed to 1 are:

@@

For CT, duplicates's flags that have been changed to 1 are:

@@

```{r Klara Wolf}

@@

###**TA analyser**
- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
